Multi-target detection with application to cryo-electron microscopy

### 2019-02-26 inverse_problems/inverse_problems.tex
Menu sentence

\TODO{Careful that $\gamma$ changed by a factor of $L$: need to modify here too.} Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$. For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$. Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$. In particular, this model allows for (additive) signal overlap. In Section~\ref{sec:poisson}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.

@@

In this section, we present three numerical experiments: \TODO{menu}.

>>>>

\TODO{Careful that $\gamma$ changed by a factor of $L$: need to modify here too.} Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$. For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$. Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$. In particular, this model allows for (additive) signal overlap. In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.

@@

In this section, we present three numerical experiments. In the first two experiments, we consider the heterogeneous model~\eqref{eq:model}. First, with a fixed noise level, we show how the estimation quality improves as the length of the observation grows. Second, we explore how many signals can be recovered in an infinite data regime, where effects of the noise have been averaged out. In the last experiment, we extend our model to 2D signals.
